MINOS Handover Plots

### 2023-12-19 minos/validation/cross_validation_default.Rmd
Adding poverty vars to handovers and cross-validation

## hhsize

@@

## housing tenure

@@

## Job Sec

```{r}
jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'job_sec')

cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
                 var = 'job_sec',
                 save = FALSE)
rm(jobsec.pivoted)
```

## Hourly Wage

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
multi_year_boxplots(raw, cv, 'hourly_wage')
q_q_comparison(raw, cv, 'hourly_wage')
```

## Children Ageing

Children ageing is now calculated in MINOS.

```{r}

format_child_age_data <- function(dataset) {
  formatted.age.data <- dataset %>%
                        dplyr::select(hidp, time, child_ages, pidp) %>%
                        filter(time >= 2014) %>%
                        group_by(time, pidp) %>%
                        summarise(child_ages = max(child_ages))

  split.ages <- strsplit(formatted.age.data$child_ages, "_")

  child.ages.expanded <- data.frame(time = rep(formatted.age.data$time, sapply(split.ages, length)), 
                                    #hidp= rep(formatted.age.data$hidp, sapply(split.ages, length)), 
                                    pidp= rep(formatted.age.data$pidp, sapply(split.ages, length)), 
                                    expanded_child_ages = as.numeric(unlist(split.ages)))

  #child.ages.expanded <- child.ages.expanded %>%
  #  group_by(pidp, time) %>%
  #  summarise(expanded_child_ages = median(expanded_child_ages))

  return (child.ages.expanded)
}

find_mode <- function(x) {
  u <- unique(x)
  tab <- tabulate(match(x, u))
  u[tab == max(tab)]
}

cv.child.ages <- format_child_age_data(cv)
cv1.child.ages <- format_child_age_data(cv1)
cv2.child.ages <- format_child_age_data(cv2)
cv3.child.ages <- format_child_age_data(cv3)
cv4.child.ages <- format_child_age_data(cv4)
cv5.child.ages <- format_child_age_data(cv5)
raw.child.ages <- format_child_age_data(raw.dat)

cv.mean.plots(cv1.child.ages, cv2.child.ages, cv3.child.ages, cv4.child.ages, cv5.child.ages, raw.child.ages, 'expanded_child_ages')
multi_year_boxplots(raw.child.ages, cv.child.ages, 'expanded_child_ages')
q_q_comparison(raw.child.ages, cv.child.ages, 'expanded_child_ages')

```

```{r} 
#nkids

format_nkids_data <- function(dataset) {
  dataset %>%
  group_by(hidp, time, pidp) %>%
  summarise(nkids = max(nkids)) %>%
  #group_by(time) %>%
  #summarise(nkids_by_year = sum(nkids_counts))
  return (dataset)
}

cv.nkids <- format_nkids_data(cv)
cv1.nkids <- format_nkids_data(cv1)
cv2.nkids <- format_nkids_data(cv2)
cv3.nkids <- format_nkids_data(cv3)
cv4.nkids <- format_nkids_data(cv4)
cv5.nkids <- format_nkids_data(cv5)
raw.nkids <- format_nkids_data(raw.dat)

cv.mean.plots(cv1.nkids, cv2.nkids, cv3.nkids, cv4.nkids, cv5.nkids, raw.nkids, 'nkids')
multi_year_boxplots(raw.nkids, cv.nkids, 'nkids')
q_q_comparison(raw.nkids, cv.nkids, 'nkids')
```

>>>>

## Household Size

@@

## Housing Tenure

@@

# CHILD POVERTY VARS

## Relative Poverty

```{r}
relative_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                   df1.name = 'simulated', 
                                                   df2 = raw, 
                                                   df2.name = 'raw', 
                                                   var = 'relative_poverty')

cv_ordinal_plots(pivoted.df = relative_poverty.pivoted, 
                 var = 'relative_poverty',
                 save = FALSE)
rm(relative_poverty.pivoted)
```

## Absolute Poverty

```{r}
absolute_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                   df1.name = 'simulated', 
                                                   df2 = raw, 
                                                   df2.name = 'raw', 
                                                   var = 'absolute_poverty')

cv_ordinal_plots(pivoted.df = absolute_poverty.pivoted, 
                 var = 'absolute_poverty',
                 save = FALSE)
rm(absolute_poverty.pivoted)
```

## Material Deprivation

```{r}
matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
                                               df1.name = 'simulated', 
                                               df2 = raw, 
                                               df2.name = 'raw', 
                                               var = 'matdep_child')

cv_ordinal_plots(pivoted.df = matdep_child.pivoted, 
                 var = 'matdep_child',
                 save = FALSE)
rm(matdep_child.pivoted)
```

## Low Income and Material Deprivation

```{r}
low_income_matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                          df1.name = 'simulated', 
                                                          df2 = raw, 
                                                          df2.name = 'raw', 
                                                          var = 'low_income_matdep_child')

cv_ordinal_plots(pivoted.df = low_income_matdep_child.pivoted, 
                 var = 'low_income_matdep_child',
                 save = FALSE)
rm(low_income_matdep_child.pivoted)
```

## Persistent Poverty

```{r}
persistent_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                     df1.name = 'simulated', 
                                                     df2 = raw, 
                                                     df2.name = 'raw', 
                                                     var = 'persistent_poverty')

cv_ordinal_plots(pivoted.df = persistent_poverty.pivoted, 
                 var = 'persistent_poverty',
                 save = FALSE)
rm(persistent_poverty.pivoted)
```

### 2023-12-19 minos/validation/handovers.Rmd
Adding poverty vars to handovers and cross-validation

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

## Poverty

### Absolute poverty

@@

### Persistent poverty

@@

### Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')

@@

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'matdep_child.png',
         plot = last_plot(),
         path = save.path)
}

>>>>

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
# out.path <- here::here('output', 'child_poverty_config/')
# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
```

@@

## CHILD POVERTY VARS

@@

### Absolute Poverty

### Persistent Poverty

@@

### Low Income and Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')

@@

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'low_income_matdep_child.png',
         plot = last_plot(),
         path = save.path)
}
